### 2016-07-03 ansi-isolation.tex
Edits.

\iso{Snapshot Isolation} ({\sc si}) proscribes this possibility. If
$T_i$ and $T_j$ both write to the same shared variable, then {\sc si}
insists that either $T_i$ be visible to $T_j$, or $T_j$ be visible to
the conflicting write of $T_i$ (this is captured by the auxiliary
definition \C{SnapshotSER}). Fig.~\ref{fig:ansi-iso-eg-si} shows an
execution where {\sc si} transaction $T_1$ witnesses a snapshot of the
database that doesn't include $T_2$. Due to \C{SI($T_1$)}, the
conflicting write to $X$ in $T_2$ is now required to witness $T_1$, as
captured by the direction of the $\visZ$ arrow (subsequent operations
also witness $T_1$ because $T_2$ is executing under {\sc mav}).
Lastly, \iso{Serializable} isolation extends $\mathtt{SnapshotSER}$ to
also cover non-conflicting transactions that write to variables read
in the current transaction.  Fig.~\ref{fig:ansi-iso-eg-ser} shows an
execution of an {\sc ser} transaction $T_3$ and a {\sc mav
transaction} $T_4$, which write to $X$ and $Y$, respectively. The
snapshot witnessed by the {\sc ser} transaction $T_3$ does not include
$T_4$, but the write to $Y$ in $T_4$, although non-conflicting,
witnesses $T_1$ because $Y$ is read by $T_1$. Visibility includes
other operations of $T_4$ because of {\sc mav}.

>>>>

\iso{Snapshot Isolation} ({\sc si}) proscribes this possibility. If
$T_i$ and $T_j$ both write to the same shared variable, then {\sc si}
insists that either $T_i$ be visible to $T_j$, or $T_j$ be visible to
the conflicting write of $T_i$ (this is captured by the auxiliary
definition \C{SnapshotSER}). Fig.~\ref{fig:ansi-iso-eg-si} shows an
execution where {\sc si} transaction $T_1$ witnesses a snapshot of the
database that doesn't include $T_2$. Due to \C{SI($T_1$)}, the
conflicting write to $X$ in $T_2$ is now required to witness $T_1$, as
captured by the direction of the $\visZ$ arrow (subsequent operations
also witness $T_1$ because $T_2$ is executing under {\sc mav}).
Lastly, \iso{Serializable} isolation extends $\mathtt{SnapshotSER}$ to
also cover non-conflicting transactions that write to variables read
in the current transaction.  Fig.~\ref{fig:ansi-iso-eg-ser} shows an
execution of an {\sc ser} transaction $T_3$ and a {\sc mav}
transaction $T_4$, which write to $X$ and $Y$, respectively. The
snapshot witnessed by the {\sc ser} transaction $T_3$ does not include
$T_4$, but the write to $Y$ in $T_4$, although non-conflicting,
witnesses $T_1$ because $Y$ is read by $T_1$. Visibility includes
other operations of $T_4$ because of {\sc mav}. Note that {\sc ser}
does not guarantee total order of transactions w.r.t. $\visZ$ because,
in reality, databases do not guarantee serializable execution unless
\emph{all} transactions choose {\sc ser}.
